A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-14 tex/codatadp.tex
more

This work is part of a larger program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, we want to implement proof
reconstruction for (co)datatype inferences in Isabelle. We also want to try
out CVC4 and its (co)datatypes for higher-order model finding in Isabelle, as
an alternative to the counterexample generator Nitpick
\cite{blanchette-nipkow-2010}. We also see some opportunities to enrich
SMT solvers with recursive and corecursive functions. Finally, it might be
possible to go further in terms of supporting nested and mixed (co)recursion
and quantified formulas over (co)datatypes in solvers.

>>>>

This work is part of a larger program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, we want to implement proof
reconstruction for CVC4's (co)datatype inferences in Isabelle. We also want to
try out CVC4 for higher-order model finding in Isabelle, as an alternative to
the counterexample generator Nitpick \cite{blanchette-nipkow-2010}. We also
see some opportunities to enrich SMT solvers with recursive and corecursive
functions. Finally, it might be possible to go further in terms of supporting
nested and mixed (co)recursion and quantified formulas over (co)datatypes in
solvers.
